%------------------------
% Ethan's Résumé Template
% Author: mauricio vancine
% License: CC-BY-4.0
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{tikz}
\input{glyphtounicode}

% font options
\usepackage[sc]{mathpazo}
\linespread{1.05}  % palladio needs more leading (space between lines)
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}  % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.1in}
\addtolength{\evensidemargin}{-0.1in}
\addtolength{\textwidth}{0.1in}
\addtolength{\topmargin}{0.1in}
\addtolength{\textheight}{0.1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% custom commands
\newcommand{\cvitem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2\\
      \small#3 & \small #4\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}\justifying}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvskill}[2]{
  \textcolor{black}{\textbf{#1}}\hfill
  \foreach \x in {1,...,5}{%
    \space{\ifnumgreater{\x}{#2}{\color{black!80!white!20}}{\color{black}}\faSquare}}\par%
  \vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}

% cor dos links
\usepackage{xcolor} % Pacote para manipulação de cores
\usepackage{hyperref} % Pacote para links

\hypersetup{
    colorlinks=true, % Ativa a coloração dos links
    linkcolor=blue, % Cor dos links internos
    urlcolor=blue,  % Cor dos links externos (URLs)
    citecolor=blue  % Cor das citações
}

\begin{document}

% contact information
\begin{center}
  \textbf{\LARGE\scshape Maurício H. Vancine}\\
  \vspace{5pt}\small
  Ecologist, Data Scientist and PhD in Ecology\\
  University of Campinas (Unicamp), Campinas, SP, Brazil\\
  \href{mailto:}{mauricio.vancine@gmail.com}
  $\ \bullet\ $ 
  \href{https://github.com/mauriciovancine}{GitHub}
  $\ \bullet\ $
  \href{https://www.linkedin.com/in/mauricio-vancine/}{LinkedIn}
    $\ \bullet\ $
  \href{https://mauriciovancine.github.io}{Website}
\end{center}

\section{Summary}
I am an ecologist focused on understanding how spatial patterns affect biodiversity. My current research explores the impact of edge effects and fires on animal-plant distribution and interactions in the Amazon, using landscape metrics and species distribution modeling (SDM) to study biodiversity changes and aid conservation.

\section{Education}
\cvheadingstart
  \cvheading
    {São Paulo State University (Unesp)}{Rio Claro, SP, Brazil}
    {PhD, Ecology, \href{https://hdl.handle.net/11449/256726}{Library}}{03/2020 - 07/2024}
  \cvheading
    {São Paulo State University (Unesp)}{Rio Claro, SP, Brazil}
    {MS, Zoology, \href{http://hdl.handle.net/11449/154993}{Library}}{03/2016 - 07/2018}
  \cvheading
    {São Paulo State University (Unesp)}{Rio Claro, SP, Brazil}
    {BS, Ecology, \href{http://hdl.handle.net/11449/138991}{Library}}{09/2011 - 03/2015}
\cvheadingend

\section{Professional Experience}
\cvheadingstart
  \cvheading
    {State University of Campinas (Unicamp)}{Campinas, SP, Brazil}
    {Postdoctoral in Spatial Ecology, LDDiv, \href{https://bv.fapesp.br/pt/auxilios/113861/interacoes-entre-plantas-e-animais-e-os-impactos-em-cascata-da-fragmentacao-da-floresta-amazonica/}{Project}}{11/2024 - Present}
\cvheadingend

\section{Technical Skills}
\cvskill{R}{5}
\cvskill{tidyverse}{4}
\cvskill{GRASS GIS}{4}
\cvskill{QGIS}{3}
\cvskill{git}{3}
\cvskill{Python}{2}
\vspace{-5pt}

\section{Publications}
\cvheadingstart
\item
\cvitemstart
  \cvitem{\href{https://orcid.org/0000-0001-9650-7575}{ORCID}}
  \cvitem{\href{https://www.webofscience.com/wos/author/record/837504}{ResearcherID}}
  \cvitem{\href{https://www.scopus.com/authid/detail.uri?authorId=57193451888}{Scopus}}
  \cvitem{\href{https://www.researchgate.net/profile/Mauricio-Vancine}{ResearchGate}}
  \cvitem{\href{https://scholar.google.com/citations?user=i-2xZBQAAAAJ}{Google Scholar}}
  \cvitem{\href{http://lattes.cnpq.br/9761288418931193}{Lattes}}
\cvitemend
\cvheadingend

\section{Languages}
\cvheadingstart
\item
\cvitemstart
  \cvitem{English (intermediate)}
  \cvitem{Spanish (basic)}
  \cvitem{Portuguese (native speaker)}
\cvitemend
\cvheadingend

\section{References}
\cvheadingstart
\item
\cvitemstart
  \cvitem{{\bf Prof. Dr. Milton Cezar Ribeiro}, milton.c.ribeiro@unesp.br, +55-19-3526-9680}
  \cvitem{{\bf Prof. Dr. Célio F. B. Haddad}, haddad1000@gmail.com, +55-19-3526-4302}
  \cvitem{{\bf Prof. Dr. Mathias Mistretta Pires},
  mathiasmpires@gmail.com, +55-19-3521-6275}
\cvitemend
\cvheadingend

\end{document}
